analysis

### 2020-06-05 analysis.Rmd
updating lab computer

### Prepare environment
```{r setup, include=FALSE}
library(bipartite)
library(mgcv)
library(mgcViz)
#library(lme4)
#library(lmerTest)
library(tidyverse)
library(lubridate)
library(GGally)
```

### Define functions
#### Colony phase breakpoint functions
```{r}
# Find breakpoints on GDD scale
breakpoints_gdd <- function(x, year, t1, t2) {

@@

#### Rarefied network analysis
```{r}
# Rare_net function: rarefies networks by iteratively subsampling more frequently sampled networks to match the transect count of the least frequently sampled one
# species level
rare_net_sp <- function(net, n, iter) {

@@

### Load site data
```{r}
site_data <- read_csv("./processed_data/site_data.csv") %>%
  dplyr::select(-c(slope.calc, slope.est, elev.min, elev.max, temp.mean)) %>% # drop these variables
  mutate(elev.class = factor(elev.class, levels = c("oben", "mitte", "unten")),
         elev.class2 = factor(elev.class2, levels = c("high", "mid", "low"))) # turn elav.class into an ordered factor
```

### Climate data
```{r}
gdd <- read_csv("./processed_data/climate.csv") %>%
  mutate(year = factor(year)) %>%
  select(site, date, gdd.cum)
```

### Colony phase breakpoint analysis
```{r}
castes <- read_csv("./processed_data/network.csv") %>%
  filter(bb.sp != "psit") %>% # We do not want to consider Psithyrus, since these parasitic species do not have a worker caste
  group_by(site, date, year, caste) %>%
  summarize(caste.count = n()) %>%
  spread(caste, caste.count) %>%
  replace(is.na(.), 0) %>%
  mutate(queen = oldqueen + queen,
         reproductive = male + youngqueen,
         q.prop = queen/(queen+worker+reproductive),
         r.prop = reproductive/(queen+worker+reproductive)) %>%
  select(-oldqueen, -youngqueen, -male) %>%
  left_join(gdd, by = c("site", "date")) %>%
  left_join(site_data, by = c("site")) %>%
  arrange(gdd.cum) %>%
  mutate(yday = yday(date))

@@

### Plot phase breakpoints
```{r}
breaks_summary <- full_join(breaks_gdd_summary, breaks_yday_summary) %>%
  select(site, date, year, elev.class2, yday, gdd.cum, break1, break2, caste, prop) %>%
  gather(time.metric, value, -c(site, date, year, elev.class2, break1, break2, caste, prop))

@@

### Load network and survey data
```{r}
bb_traits <- read_csv("./processed_data/bb_traits.csv") %>%
  select(subgenus, bb.sp, pbl.w, pbl.w.class)

@@

survey <- read_csv("./processed_data/floral_survey.csv") %>%
  mutate(year = factor(year)) %>% # convert year to factor
  #semi_join(net, by = c("site", "plant.sp")) %>% # Consider only plants visited at a given site-date
  left_join(gdd, by = c("site", "date")) %>%
  left_join(breaks, by = c("site", "year")) %>%
  left_join(site_data, by = "site") %>%
  ungroup() %>%
  mutate(phase = case_when(
    gdd.cum < break1.gdd ~ "founding",
    gdd.cum >= break1.gdd & gdd.cum < break2.gdd ~ "buildup",
    gdd.cum > break2.gdd ~ "reproductive"
  )) %>%
  mutate(phase = factor(phase, levels = c("founding", "buildup", "reproductive"))) %>%
  arrange(site, date)
```
### BB and floral turnover ~ elevation
```{r}
bb_range <- net %>%
  group_by(site, elev.mean, bb.sp) %>%
  summarize(abund = n()) %>%
  group_by(bb.sp) %>%
  mutate(elev.floor = min(elev.mean),
         elev.ceiling = max(elev.mean),
         elev.range = elev.ceiling - elev.floor,
         elev.med = elev.floor + ((elev.ceiling - elev.floor)/2))

@@

ggplot(bb_range, aes(reorder(bb.sp, elev.med), elev.mean)) +
  geom_line(size = 3, color = "gray60") +
  geom_point(aes(size = abund), alpha = 0.5) +
  theme_light(14) +
  xlab("BB species") +
  ylab("Elevation") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### BB abundance, diversity, and per-capita resource availability
```{r eval=FALSE, echo=FALSE}
### Per-transect Bombus density
bb_abund <- net %>%
  group_by(site, date, dayofyear, gdd.cum, year, elev.class2, 
           elev.mean, break1.gdd, break2.gdd) %>%
  summarize(bb.abund = n())

@@

abund_div_mean <- abund_div %>%
  select(-dayofyear, -week, -month, -break1.gdd, -break2.gdd) %>%
  gather(metric, value, -c(site, date, gdd.cum, year, elev.class2, elev.mean, phase)) %>%
  group_by(site, year, elev.class2, elev.mean, metric) %>%
  summarize(value = mean(value, na.rm = TRUE))

### BB abundance ~ floral abundance
ggplot(abund_div, aes(log(fl.abund), bb.abund, color = year)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("BB abundance") +
  xlab("log(floral cover)") +
  theme_bw()

@@

@@

@@

### GAM surface plots of abundance and diversity metrics
#### HGAM elevation x time x year (I would really like someone -- maybe my future self -- to check that I'm doing this right)
##### Floral abundance
```{r}
fl_abund_yday <- gam(fl.abund ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    family = "tw",
                    method = "REML")

@@

##### Floral richness
```{r}
fl_rich_yday <- gam(fl.rich ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    method = "REML")

@@

##### BB abundance
```{r}
bb_abund_yday <- gam(bb.abund ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    method = "REML")

@@

##### BB richness
```{r}
bb_rich_yday <- gam(bb.rich ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    method = "REML")

@@

### Rarefied network analysis (not broken down by phase)
```{r}
### Determine the minimum transect count per site*year to set rarefaction sampling
transects <- net %>%
  select(site, year, date) %>%
  unique()

@@

#### Community mean d
ggplot(filter(spmet_mean, metric == "d"), aes(elev.mean, value)) +
  geom_point(aes(color = year)) +
  geom_smooth(method = "gam", formula = y ~ s(x), color = "black", linetype = "dashed", size = 0.75) +
  xlab("Elevation") +
  ylab("Community mean d'") +
  theme_light(16)

@@

### Let's look at how abundance varies on a per-species basis
```{r}
species <- net %>%
  group_by(site, date, year, dayofyear, gdd.cum, phase, elev.mean, elev.class2, bb.sp, subgenus, pbl.w, pbl.w.class) %>%
  summarize(abund = n()) %>%
  group_by(site, date) %>%
  mutate(prop = abund/sum(abund))

@@

### Plot some dang networks
```{r}
web <- net %>%
  group_by(year, elev.class2, phase, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
  summarize(freq = n()) %>%
  unite(webID, c(year, elev.class2, phase), sep = "_") %>% # calculate interaction frequency per species pair within each site
  dplyr::select(higher = bb.sp, lower = plant.sp, webID, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs()  # convert to to bipartite web

@@

### Per-transect network analysis -- is it worth it? I would have to filter out the transects for which the networks are too small.
#### Network level
```{r}
per.transect_netmet <- net %>%
  group_by(site, dayofyear, gdd.cum, year, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
  summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
  group_by(site, dayofyear, gdd.cum, year) %>%
  mutate(size = sum(freq),
         bb.rich = length(unique(bb.sp)),
         fl.rich = length(unique(plant.sp)),
         total.rich = bb.rich + fl.rich) %>%
  filter(bb.rich > 1 & fl.rich > 1) %>%
  unite(webID, c(site, dayofyear, gdd.cum, year, size), sep = "_") %>%
  dplyr::select(higher = bb.sp, lower = plant.sp, webID, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs() %>% # convert to to bipartite web
  map(networklevel, weighted = TRUE, level = "higher", index = c("web asymmetry", "weighted NODF", "niche overlap", "C score", "H2")) %>% # We probably care mainly about the BB level of the network
  data.frame() %>%
  t() %>%
  data.frame() %>%
  rownames_to_column() %>%
  dplyr::select(id = rowname, everything()) %>%
  as_tibble() %>%
  gather(metric, value, -id) %>%
  separate(id, into = c("site", "yday", "gdd.cum", "year", "size"), sep = "_") %>%
  mutate(size = as.numeric(size),
         year = factor(year),
         gdd.cum = as.numeric(gdd.cum),
         yday = as.numeric(yday),
         site = as.factor(site)) %>%
  left_join(site_data) %>%
  left_join(abund_div)

@@

#### Species level
```{r}
per.transect_spmet <- net %>%
  group_by(site, dayofyear, gdd.cum, year, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
  summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
  group_by(site, dayofyear, gdd.cum, year) %>%
  mutate(size = sum(freq),
         bb.rich = length(unique(bb.sp)),
         fl.rich = length(unique(plant.sp)),
         total.rich = bb.rich + fl.rich) %>%
  filter(bb.rich > 1 & fl.rich > 1) %>%
  unite(webID, c(site, dayofyear, gdd.cum, year, size), sep = "_") %>%
  dplyr::select(higher = bb.sp, lower = plant.sp, webID, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs() %>% # convert to to bipartite web
  map(specieslevel, level = "higher", index = "d") %>% # We probably care mainly about the BB level of the network
  map(rownames_to_column) %>%
  map(as_tibble) %>%
  bind_rows(.id = "id") %>% # Collapse list into big data frame
  rename(sp = rowname) %>%
  gather(metric, value, -c(sp, id)) %>% # get mean value across iterations for each metric
  separate(id, sep = "_", into = c("site", "yday", "gdd.cum", "year", "size")) %>%
  mutate(size = as.numeric(size),
         year = factor(year),
         gdd.cum = as.numeric(gdd.cum),
         yday = as.numeric(yday)) %>%
  left_join(site_data) %>%
  left_join(bb_traits, by = c("sp" = "bb.sp")) %>%
  left_join(abund_div)

@@

### Phase x elev network analysis
```{r}
### Prepare pxe abundance and diversity table
pxe_abund_div <- abund_div %>%
  select(-gdd.cum, -yday, -week, -month, -date, -elev.class2) %>%
  gather(ad.metric, ad.value, -c(site, year, phase, elev.mean)) %>%
  group_by(site, phase, year, ad.metric) %>%
  summarize(ad.value = mean(ad.value, na.rm = TRUE))

>>>>

### Prepare environment
```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(bipartite)
library(mgcv)
library(mgcViz)
#library(lme4)
#library(lmerTest)
library(tidyverse)
library(lubridate)
library(GGally)
```

### Define functions
#### Colony phase breakpoint functions
```{r include=FALSE}
# Find breakpoints on GDD scale
breakpoints_gdd <- function(x, year, t1, t2) {

@@

#### Rarefied network analysis
```{r, include=FALSE}
# Rare_net function: rarefies networks by iteratively subsampling more frequently sampled networks to match the transect count of the least frequently sampled one
# species level
rare_net_sp <- function(net, n, iter) {

@@

### Load site data
```{r, include=FALSE}
site_data <- read_csv("./processed_data/site_data.csv") %>%
  dplyr::select(-c(slope.calc, slope.est, elev.min, elev.max, temp.mean)) %>% # drop these variables
  mutate(elev.class = factor(elev.class, levels = c("oben", "mitte", "unten")),
         elev.class2 = factor(elev.class2, levels = c("high", "mid", "low"))) # turn elav.class into an ordered factor
```

### Climate data
```{r, include=FALSE}
gdd <- read_csv("./processed_data/climate.csv") %>%
  mutate(year = factor(year)) %>%
  select(site, date, gdd.cum)
```

### Colony phase breakpoint analysis
```{r, include=FALSE}
castes <- read_csv("./processed_data/network.csv") %>%
  filter(bb.sp != "psit") %>% # We do not want to consider Psithyrus, since these parasitic species do not have a worker caste
  group_by(site, date, year, caste) %>%
  summarize(caste.count = n()) %>%
  spread(caste, caste.count) %>%
  replace(is.na(.), 0) %>%
  mutate(queen = oldqueen + queen,
         reproductive = male + youngqueen,
         q.prop = queen/(queen+worker+reproductive),
         r.prop = reproductive/(queen+worker+reproductive)) %>%
  select(-oldqueen, -youngqueen, -male) %>%
  left_join(gdd, by = c("site", "date")) %>%
  left_join(site_data, by = c("site")) %>%
  arrange(gdd.cum) %>%
  mutate(yday = yday(date))

@@

### Plot phase breakpoints
```{r, include=FALSE}
breaks_summary <- full_join(breaks_gdd_summary, breaks_yday_summary) %>%
  select(site, date, year, elev.class2, yday, gdd.cum, break1, break2, caste, prop) %>%
  gather(time.metric, value, -c(site, date, year, elev.class2, break1, break2, caste, prop))

@@

### Load network and survey data
```{r, include=FALSE}
bb_traits <- read_csv("./processed_data/bb_traits.csv") %>%
  select(subgenus, bb.sp, pbl.w, pbl.w.class)

@@

survey <- read_csv("./processed_data/floral_survey.csv") %>%
  mutate(year = factor(year)) %>% # convert year to factor
  #semi_join(net, by = c("site", "plant.sp")) %>% # Consider only plants visited at a given site-date
  left_join(gdd, by = c("site", "date")) %>%
  left_join(breaks, by = c("site", "year")) %>%
  left_join(site_data, by = "site") %>%
  ungroup() %>%
  mutate(phase = case_when(
    gdd.cum < break1.gdd ~ "founding",
    gdd.cum >= break1.gdd & gdd.cum < break2.gdd ~ "buildup",
    gdd.cum > break2.gdd ~ "reproductive"
  )) %>%
  mutate(phase = factor(phase, levels = c("founding", "buildup", "reproductive"))) %>%
  arrange(site, date)
```
### BB and floral turnover ~ elevation
```{r, include=FALSE}
bb_range <- net %>%
  group_by(site, elev.mean, bb.sp) %>%
  summarize(abund = n()) %>%
  group_by(bb.sp) %>%
  mutate(elev.floor = min(elev.mean),
         elev.ceiling = max(elev.mean),
         elev.range = elev.ceiling - elev.floor,
         elev.med = elev.floor + ((elev.ceiling - elev.floor)/2))

@@

ggplot(bb_range, aes(reorder(bb.sp, elev.med), elev.mean)) +
  geom_line(size = 3, color = "gray60") +
  geom_point(aes(size = abund), alpha = 0.5) +
  theme_light(14) +
  xlab("BB species") +
  ylab("Elevation") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

### Plot only the plants that drop out at 1750 m
ggplot(filter(fl_net_elev, sites > 0 & elev.ceiling < 1750), 
       aes(reorder(plant.sp, elev.med), elev.mean)) +
  geom_line(size = 1, color = "gray60") +
  geom_point(alpha = 0.5, aes(size = abund)) +
  theme_light(8) +
  xlab("Plant species") +
  ylab("Elevation") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(filter(fl_survey_elev, sites > 0 & elev.ceiling < 1750), 
       aes(reorder(plant.sp, elev.med), elev.mean)) +
  geom_line(size = 1, color = "gray60") +
  geom_point(alpha = 0.5, aes(size = abund)) +
  theme_light(8) +
  xlab("Plant species") +
  ylab("Elevation") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### BB abundance, diversity, and per-capita resource availability
```{r eval=FALSE, echo=FALSE, include=FALSE}
### Per-transect Bombus density
bb_abund <- net %>%
  group_by(site, date, dayofyear, gdd.cum, year, elev.class2, 
           elev.mean, break1.gdd, break2.gdd) %>%
  summarize(bb.abund = n())

@@

abund_div_mean <- abund_div %>%
  select(-dayofyear, -week, -month, -break1.gdd, -break2.gdd) %>%
  gather(metric, value, -c(site, date, gdd.cum, year, elev.class2, elev.mean, phase)) %>%
  group_by(site, year, elev.class2, elev.mean, metric) %>%
  summarize(value = mean(value, na.rm = TRUE))
```

### Plotting abundance and diversity patterns
```{r}
### BB abundance ~ floral abundance
ggplot(abund_div, aes(log(fl.abund), bb.abund, color = year)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE) +
  facet_grid(elev.class2 ~ phase, scales = "free") +
  ylab("BB abundance") +
  xlab("log(floral cover)") +
  theme_bw()

@@

ggplot(abund_div, aes(elev.mean, fl.rich)) +
  geom_point(alpha = 0.5, aes(color = year)) +
  geom_smooth(color = "black", linetype = "dashed", size = 0.75) +
  theme_light(16) +
  xlab("Elevation") +
  ylab("Floral abundance")

@@

ggplot(abund_div, aes(elev.mean, log(fl.abund), color = year)) +
  geom_point(alpha = 0.5) +
  geom_smooth() +
  theme_light()

ggplot(abund_div, aes(elev.mean, fl.abund)) +
  geom_point(alpha = 0.5, aes(color = year)) +
  geom_smooth(color = "black", linetype = "dashed", size = 0.75) +
  theme_light(16) +
  xlab("Elevation") +
  ylab("Floral abundance")

ggplot(abund_div, aes(elev.mean, log(fl.abund))) +
  geom_point(alpha = 0.5, aes(color = year)) +
  geom_smooth(color = "black", linetype = "dashed", size = 0.75) +
  theme_light(16) +
  xlab("Elevation") +
  ylab("log(Floral abundance)")

@@

### GAM surface plots of abundance and diversity metrics
#### HGAM elevation x time x year (I would really like someone -- maybe my future self -- to check that I'm doing this right)
##### Floral abundance
```{r eval=FALSE, include=FALSE}
fl_abund_yday <- gam(fl.abund ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    family = "tw",
                    method = "REML")

@@

##### Floral richness
```{r eval=FALSE, include=FALSE}
fl_rich_yday <- gam(fl.rich ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    method = "REML")

@@

##### BB abundance
```{r eval=FALSE, include=FALSE}
bb_abund_yday <- gam(bb.abund ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    method = "REML")

@@

##### BB richness
```{r eval=FALSE, include=FALSE}
bb_rich_yday <- gam(bb.rich ~ year +
                    te(yday, elev.mean, by=year, bs= c("cc", "tp"), k=c(10, 10), m=1),
                    data = filter(abund_div),
                    method = "REML")

@@

### Rarefied network analysis (not broken down by phase)
```{r, include = FALSE}
### Determine the minimum transect count per site*year to set rarefaction sampling
transects <- net %>%
  select(site, year, date) %>%
  unique()

@@

#### Community mean d
ggplot(filter(spmet_mean, metric == "d"), aes(elev.mean, value)) +
  geom_point(aes(color = year)) +
  geom_smooth(method = "gam", formula = y ~ s(x, k = 10), color = "black", linetype = "dashed", size = 0.75) +
  xlab("Elevation") +
  ylab("Community mean d'") +
  theme_light(16)

@@

### Let's look at how abundance varies on a per-species basis
```{r eval=FALSE, include=FALSE}
species <- net %>%
  group_by(site, date, year, dayofyear, gdd.cum, phase, elev.mean, elev.class2, bb.sp, subgenus, pbl.w, pbl.w.class) %>%
  summarize(abund = n()) %>%
  group_by(site, date) %>%
  mutate(prop = abund/sum(abund))

@@

### Plot some dang networks
```{r eval=FALSE, include=FALSE}
web <- net %>%
  group_by(year, elev.class2, phase, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
  summarize(freq = n()) %>%
  unite(webID, c(year, elev.class2, phase), sep = "_") %>% # calculate interaction frequency per species pair within each site
  dplyr::select(higher = bb.sp, lower = plant.sp, webID, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs()  # convert to to bipartite web

@@

### Per-transect network analysis -- is it worth it? I would have to filter out the transects for which the networks are too small.
#### Network level
```{r eval=FALSE, include=FALSE}
per.transect_netmet <- net %>%
  group_by(site, dayofyear, gdd.cum, year, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
  summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
  group_by(site, dayofyear, gdd.cum, year) %>%
  mutate(size = sum(freq),
         bb.rich = length(unique(bb.sp)),
         fl.rich = length(unique(plant.sp)),
         total.rich = bb.rich + fl.rich) %>%
  filter(bb.rich > 1 & fl.rich > 1) %>%
  unite(webID, c(site, dayofyear, gdd.cum, year, size), sep = "_") %>%
  dplyr::select(higher = bb.sp, lower = plant.sp, webID, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs() %>% # convert to to bipartite web
  map(networklevel, weighted = TRUE, level = "higher", index = c("web asymmetry", "weighted NODF", "niche overlap", "C score", "H2")) %>% # We probably care mainly about the BB level of the network
  data.frame() %>%
  t() %>%
  data.frame() %>%
  rownames_to_column() %>%
  dplyr::select(id = rowname, everything()) %>%
  as_tibble() %>%
  gather(metric, value, -id) %>%
  separate(id, into = c("site", "yday", "gdd.cum", "year", "size"), sep = "_") %>%
  mutate(size = as.numeric(size),
         year = factor(year),
         gdd.cum = as.numeric(gdd.cum),
         yday = as.numeric(yday),
         site = as.factor(site)) %>%
  left_join(site_data) %>%
  left_join(abund_div)

@@

#### Species level
```{r eval=FALSE, include=FALSE}
per.transect_spmet <- net %>%
  group_by(site, dayofyear, gdd.cum, year, bb.sp, plant.sp) %>% # group by site, date, bee species, plant species
  summarize(freq = n()) %>% # calculate interaction frequency per species pair within each site
  group_by(site, dayofyear, gdd.cum, year) %>%
  mutate(size = sum(freq),
         bb.rich = length(unique(bb.sp)),
         fl.rich = length(unique(plant.sp)),
         total.rich = bb.rich + fl.rich) %>%
  filter(bb.rich > 1 & fl.rich > 1) %>%
  unite(webID, c(site, dayofyear, gdd.cum, year, size), sep = "_") %>%
  dplyr::select(higher = bb.sp, lower = plant.sp, webID, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs() %>% # convert to to bipartite web
  map(specieslevel, level = "higher", index = "d") %>% # We probably care mainly about the BB level of the network
  map(rownames_to_column) %>%
  map(as_tibble) %>%
  bind_rows(.id = "id") %>% # Collapse list into big data frame
  rename(sp = rowname) %>%
  gather(metric, value, -c(sp, id)) %>% # get mean value across iterations for each metric
  separate(id, sep = "_", into = c("site", "yday", "gdd.cum", "year", "size")) %>%
  mutate(size = as.numeric(size),
         year = factor(year),
         gdd.cum = as.numeric(gdd.cum),
         yday = as.numeric(yday)) %>%
  left_join(site_data) %>%
  left_join(bb_traits, by = c("sp" = "bb.sp")) %>%
  left_join(abund_div)

@@

### Phase x elev network analysis
```{r eval=FALSE, include=FALSE}
### Prepare pxe abundance and diversity table
pxe_abund_div <- abund_div %>%
  select(-gdd.cum, -yday, -week, -month, -date, -elev.class2) %>%
  gather(ad.metric, ad.value, -c(site, year, phase, elev.mean)) %>%
  group_by(site, phase, year, ad.metric) %>%
  summarize(ad.value = mean(ad.value, na.rm = TRUE))
